\documentclass[]{resume}

\usepackage{amsmath}
\usepackage{hyperref}

% Set applicant's personal data for header
\name{Clayton R. Castro}
\address{10982 Roebling Avenue, Unit 110 \linebreak Los Angeles CA 90024}
\contacts{(951) 387-9310 \linebreak hello@claytonc.dev \linebreak \href{https://claytonc.dev}{\textit{claytonc.dev}}}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Product Engineer, Intern}{Rancher Government Solutions}{Fall 2022 -- Present}
			Carbide Registry Portal
			\begin{itemize}
				\item Designed and implemented a Go-based REST API to manage the product database and thousands of OCI container images, enabling internal Tekton build pipelines and customer-facing applications.
				\item Designed and implemented a Nuxt.js-based frontend to provide customers with an intuitive UI for browsing the product catalog and downloading tarballs from S3 for air-gapped deployments. Includes a custom SBOM viewer for analyzing software package dependencies across all container images in the registry.
                \item Securely containerized the application and developed an accompanying Helm chart; oversaw its successful production rollout.
			\end{itemize}
            Carbide Account Provisioner
            \begin{itemize}
                \item Created a Vue-based frontend for managing Harbor registry robot accounts, improving efficiency for the support engineering team. Securely containerized the application and developed an accompanying Helm chart.
            \end{itemize}
			Releasebot
			\begin{itemize}
                \item Developed a Go-based event-driven daemon to monitor GitHub repositories for new releases, triggering \mbox{automated} internal build pipelines via custom HTTP payloads.
                \item Securely containerized the application and developed an accompanying Helm chart.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Recreation Leader/Lifeguard}{City of Murrieta}{Summer 2017 -- Fall 2022}	
			\begin{itemize}
				\item Oversaw pool/youth center activities while handling day-to-day transactions and security.
                \item Taught private and general swim lessons for individuals of all ages.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Los Angeles, CA}{University of California - Los Angeles}{Fall 2022 -- Spring 2025}
            B.S. in Computer Science
			\begin{itemize}
				\item Notable Coursework: Operating Systems Principles; Natural Language Processing; Programming Languages; Computer Network Fundamentals
			\end{itemize}
		\end{cvsubsection}
        
        \begin{cvsubsection}{Menifee, CA}{Mt. San Jacinto College}{Winter 2021 -- Spring 2022}
            \begin{itemize}
                \item Accolades: Dean's List, Honors Program Graduate
                \item Notable Coursework: Linear Algebra, Computer Organization \& Assembly Language, Multivariable Calculus
            \end{itemize}
        \end{cvsubsection}
    
        \begin{cvsubsection}{Fort Worth, TX}{Texas Christian University}{Fall 2019 -- Spring 2020}
            \begin{itemize}
                \item Accolades: Dean's List, TCU Scholar
                \item Notable Positions: Economics Club - Treasurer, D1 NCAA Cross Country and Track Team Athlete
            \end{itemize}
        \end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
            \item \textbf{Homelab} (2020 - Present) Self-hosted Kubernetes cluster on consumer-grade hardware - completely managed through GitOps via FluxCD. I use this cluster to test/deploy my own software as well as host a number of publicly facing services. For currently deployed software see: \href{https://github.com/clanktron/homelab}{\textit{github.com/clanktron/homelab}}
                \item \textbf{spdx-types} (2024) TypeScript library for handling SBOMs in SPDX (Software Package Data Exchange) json format. \href{https://github.com/clanktron/spdx-types}{\textit{github.com/clanktron/spdx-types}}
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Languages: Go, TypeScript/JavaScript, Lua, POSIX Shell, Fish Shell, C, C++, Python, SQL, LaTeX, Java, Ocaml, Assembly (x86, MIPS, RISC-V), Rust
				\item Tooling: Linux, Git, Kubernetes, Docker, Neovim/Vim, FluxCD, Crossplane, Terraform
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
